\documentclass{article}

\begin{document}
\title{CS352 - Project 1 Report}
\author{Arun Felix and Bhavya Patel}
\maketitle

\section{Team Details}

\begin{center}
    \begin{itemize}
        \item Arun Felix (netid: ajf277)
        \item Bhavya Patel (netid: bsp75)
    \end{itemize}    
\end{center}

\section{Collaboration}

We used the Python documentation, and Bhavya focused on the first half. I did the last half and developed testcases.

\section{Observations after step 2}

In step two, we removed the time.sleep(5) statement. Notice that the program will not behave consistently. 

\begin{itemize}
    \item First, multithreading is inconsistent, and the behavior of multithreaded programs is inconsistent.
    \begin{itemize}
        \item The main function can finish before the threads finish.
        \item We can fix this using the join function, so ensure the program stops only after the client and server threads are complete.
    \end{itemize}
    \item Second, the server might not be able to bind to a particular port number since it takes time to free the port number.
    \begin{itemize}
        \item This is after running the program consistently.
    \end{itemize}
\end{itemize}

\section{Difficulties}

We didn't face any difficulties.

\section{Design decisions}

\begin{itemize}
    \item Because waiting for the port to free up is cumbersome, we implemented a function for the server to wait until the port becomes available.
\end{itemize}

\section{Testing}
\begin{itemize}
    \item We put all tests in the tests folder.
    \item We created a tests.py file with the client and server functions. We call the server and client functions with an input file, an output file, and an expected output file.
    \item We tested a couple of corner cases, like having an empty file, which behaves as intended, giving an empty output file.
\end{itemize}

\section{What'd we learn?}

\begin{itemize}
    \item This project helped us understand why we need sockets and what binding and listening do.
    \begin{itemize}
        \item Systems Programming taught sockets, but it was slightly complex, requiring us to use multithreading explicitly.
        \item The Python socket interface provided many abstractions over C's socket interface.
    \end{itemize}
    \item We also learned about the netstat utility on UNIX systems.
\end{itemize}

\end{document}